Deriving an Executable Model of a Data Stream Protocol from its Specification

### 2009-07-29 papers/ModelBasedTestCaseGenerationDataStreamProtocol/paper.tex
paper ModelBasedTestCaseGenerationDataStreamProtocol structure

\begin{verbatim}
OBJECTIVE: 
Specifications used as a blueprint for system development.
Specifications to generate test suite to validate the developed system.
Specifications to validate simulator of the developed system.
Apply to data stream processing: verify the stream is parsed correctly, 
verify the parsed stream output stream can be simulated.

@@

CONCLUSIONS:
Specifications serves two purposes, and indirectly a third one.
\end{verbatim}

  Sensor packages typically communicate (control sensors and report
  sensor measurements) with a streaming packet-based network protocol.
  The \ST device is an example of such a sensor package, as it
  communicates with an arbitrary computer system (running Linux or
  Windows, at the moment) over a USB bus using a streaming
  packet-based protocol.  This sensor platform is a custom-designed,
  but inexpensive, sensor platform (called the \ST) paired with
  general-purpose small-scale compute nodes, including everything from
  low-power PDAs to powerful touchscreen-based portable computers.
  There are over a dozen sensors on the \ST itself, and new sensors
  can be added by adding them to the USB bus.  A third-party low-level
  C driver, provided by the USB chip vendor, creates and parses
  generic USB communication packets, and a custom medium-level Java
  driver creates and parses \ST streaming communication packets.  This
  latter Java driver is formally specified, validated with rigorous
  unit testing, and verified using extended static checking.  However,
  because of this process and combination of technologies, using this
  specification we are able to both communicate with a real \ST
  \textbf{and} generate a formally specified, executable, functional
  model-based specification for the protocol itself written in the
  Java Modeling Language.  This protocol model is itself an executable
  stream simulator that can be used to develop new \ST user
  applications without having the \ST hardware at all.  Consequently,
  from this single specification, we can test that the \ST hardware
  communicates as expected, test that our \ST simulator communicates
  as expected, and simulate the \ST protocol stream itself.

@@

%======================================================================
\Section{Introduction}

@@

%=====================================================================
\Section{Conclusion}

A conclusion.

>>>>

\begin{verbatim}

OBJECTIVE: 
Specifications used as a blueprint for system development.
Specifications to generate test suite to validate the developed system.
Specifications to validate simulator of the developed system.
Apply to data stream processing: verify the stream is parsed correctly, 
verify the parsed stream output stream can be simulated.

@@

CONCLUSIONS:
Specifications serves two purposes, and indirectly a third one.

\end{verbatim}

  Sensor packages typically communicate (control sensors and report
  sensor measurements) with a streaming packet-based network protocol.
  The \ST device is an example of such a sensor package, as it
  communicates with an arbitrary computer system (running Linux or
  Windows, at the moment) over a USB bus using a streaming
  packet-based protocol. 
  This sensor platform is a custom-designed,
  but inexpensive, sensor platform (called the \ST) paired with
  general-purpose small-scale compute nodes, including everything from
  low-power PDAs to powerful touchscreen-based portable computers.
  There are over a dozen sensors on the \ST itself, and new sensors
  can be added by adding them to the USB bus.
  A third-party low-level
  library, provided by the USB chip vendor, creates and parses
  generic USB communication packets, while a custom medium-level Java
  driver creates and parses \ST streaming communication packets. 
  This
  latter Java driver is formally specified, validated with rigorous
  unit testing, and verified using extended static checking. 
  Because of this process and combination of technologies, using this
  specification we are able to both communicate with a real \ST
  \textbf{and} generate a formally specified, executable, functional
  model-based specification for the protocol itself written in the
  Java Modeling Language.
  \todo executable? how? what does this mean?
  This protocol model is itself an executable
  stream simulator that can be used to develop new \ST user
  applications without having the \ST hardware at all. 
  Consequently,
  from this single specification, we can test that the \ST hardware
  communicates as expected, test that our \ST simulator communicates
  as expected, and simulate the \ST protocol stream itself.

@@

%======================================================================
\section{Introduction}

@@

\todo extend

\paragraph*{Outline}

In section \ref{sec:data_stream_and_protocol_model} the data stream model 
and protocol is presented, we will give both a higl level overview of the 
protocol, and a formalized, JML based, specification,

In section \ref{sec:test_cases} the test cases structure is presented, for 
both the hand made and the generated ones. 
Both the approaches are analyzed, their pro and contro are discussed, as 
well as the expected advantages to use them in combination.

In section \ref{sec:test_cases} the test cases structure is presented, for 
both the hand made and the generated ones. 
Both the approaches are analyzed, their pro and contro are discussed, as 
well as the expected advantages to use them in combination.

In section \ref{sec:test_cases_on_the_job} the execution of the test suites
is described, and the results are analyzed and compared, both from qualitative
and quantitative points of view.

In section \ref{sec:test_cases_and_the_scenarios} we examine the different 
scenarios on which test cases based on specifications can be applied, and 
the resulting benefits it is possible to obtain.

In section \ref{sec:related_works} related works are presented and analyzed.

Finally in section \ref{sec:conclusions} we outline some conclusions and we 
briefly describe our ongoing and future works on similar topics.

%=====================================================================
\section{Data stream and protocol model}
\label{sec:data_stream_and_protocol_model}

\todo describe package

\todo describe high level representation of package: sensors and data 
details remains, exact package structure and sensor data location in the
packege are lost

\todo describe JML specification of the high levelr representation of the 
package

%=====================================================================
\section{Test cases}
\label{sec:test_cases}

\todo describe dual approach: hand made tests + generated from 
specification tests

\todo describe hybrid agile and TDD approach: high level informal 
specifications with BON, iterative refinements of code, to distill 
test cases and formal specification of the interfaces

\todo describe the necessity to add specification generated tests: to ensure
that specification is sound, to obtain higher coverage

\paragraph*{Hand made tests}

\todo describe hand made tests structure

\todo describe abstract test case and abstract test suite patterns: how to 
write tests against interfaces and/or abstract classes

\paragraph*{Generated tests}

\todo describe the tool that generates the testing

\todo describe the structure of the generates tests

%=====================================================================
\section{Test cases on the job}
\label{sec:test_cases_on_the_job}

\todo report high level analysis of the test suites

\todo describe measures: coverage, number of new bugs found

\todo compare hand made vs generated tests

\todo compare compare coupled approach vs single approaches

%=====================================================================
\section{Test cases and the scenarios}
\label{sec:test_cases_and_the_scenarios}

\todo benefit: the approch can be used to test different part of the system
that share the same specification

\todo testing the stream

\todo testing the simulator

\todo describe general approach: depending at what level (of abstraction) tests 
and specifications are written, it is possible to verify both the simulator and 
the real protocol (isn't this obvious?)

%=====================================================================
\section{Related works}
\label{sec:related_works}

\todo

%=====================================================================
\section{Conclusion}
\label{sec:conclusion}

\todo
